---
title: "Python Cleaning"
format: 
  html:
    toc: true
    toc-location: left
    toc-depth: 3
    number-sections: true
    code-fold: false
    embed-resources: true
execute: 
  warning: false
editor: 
  markdown: 
    wrap: 72
---

# Introduction

In this Quarto document, we present the code that was used to prepare Python data from our database into a single data frame to be used for analysis. The final Python data frame is at the user level, and contains no information for maintainer level analysis. 

```{r, message=FALSE, eval=FALSE}
library(tidyverse)
library(RMySQL)
library(ggwes)
library(knitr)
library(kableExtra)
library(pander)
library(ggthemes)
library(tidyorgs)
library(diverstidy)
```

# File List

## Input Files

```{r, include=FALSE, eval=FALSE}
# load in the downloads by year
con <- dbConnect(MySQL(), user = "admin", password = "OSS022323",
    dbname = "python", host = "oss-1.cij9gk1eehyr.us-east-1.rds.amazonaws.com")
```

-   python_dependencies: PyPi package dependencies

-   python_repos: PyPi GitHub repos loaded from database containing repository metrics

-   python_github: PyPi GitHub packages

-   python_commits: PyPi GitHub user commit data containing additions and deletions as well as location data

```{r, eval=FALSE}
python_dependencies <- read.csv("\\\\westat.com\\DFS\\DVSTAT\\Individual Directories\\Askew\\Paper_Data\\python_dependencies.csv") %>%
            select(-X)

python_repos <- read.csv("\\\\westat.com\\DFS\\DVSTAT\\Individual Directories\\Askew\\Paper_Data\\python_repos.csv") %>%
            select(-X)

python_github <- read.csv("\\\\westat.com\\DFS\\DVSTAT\\Individual Directories\\Askew\\Paper_Data\\python_github.csv") %>%
            select(-X)

python_commits <- read.csv("\\\\westat.com\\DFS\\DVSTAT\\Individual Directories\\Askew\\Paper_Data\\python_user_commits.csv") %>%
            select(-X)

```


```{r, eval=FALSE}
### create slug variable for github packages
python_dependencies <- python_github %>%
  mutate(slug = paste0(Owner, "/", Repo)) %>%
  select(-Owner, -Repo)%>%
  left_join(python_dependencies, by = "Package")


### create slug variable for commit data
python_commits <- python_commits %>%
  mutate(slug = paste0(repo_owner, "/", repo_name)) %>%
  select(-repo_owner, -repo_name)

### create slug variable for repo data
python_repos <- python_repos %>%
  mutate(slug = paste0(owner, "/", repo)) %>%
  select(-owner, -repo)

### aggregate python data by total additions
python_commits_total <- python_commits %>%
  group_by(slug, author_user_login) %>%
  mutate(total_additions = sum(additions)) %>%
  arrange(slug, author_user_login) %>%
  slice(1) %>%
  ungroup()
```

## Data Methods

### Extracting and cleaning organizations

The organization is extracted from the author email in the commits dataframe and then the tidyorgs package is used to categorize the email as belonging to either government, academic, nonprofit, or business. The data is saved in an object titled “Inst" and this is joined to the commits dataframe.

```{r, eval=FALSE}
user_emails_to_orgs1 <- python_commits_total %>%
  email_to_orgs(author_email, input = author_email, output = Institution, "government")

user_emails_to_orgs2 <- python_commits_total %>%
  email_to_orgs(author_email, input = author_email, output = Institution, "academic") 

user_emails_to_orgs3 <- python_commits_total %>%
  email_to_orgs(author_email, input = author_email, output = Institution, "nonprofit") 

user_emails_to_orgs4 <- python_commits_total %>%
  email_to_orgs(author_email, input = author_email, output = Institution, "business") 

# creating an identifier variable for type of institution

user_emails_to_orgs1$Sector <- "Government"

user_emails_to_orgs2$Sector <- "Academic"

user_emails_to_orgs3$Sector <- "Nonprofit"

user_emails_to_orgs4$Sector <- "Business"

# Binding to one dataframe

Inst <- as.data.frame(rbind(user_emails_to_orgs1, user_emails_to_orgs2, 
                            user_emails_to_orgs3, user_emails_to_orgs4))

# Filtering for distinct emails
Inst_filtered <- Inst %>%
                        distinct(author_email, .keep_all = T)

python_commits_total <- python_commits_total %>% left_join(Inst_filtered, by = "author_email")

## replace Na with Unknown in sector and institution

# Replace NA values in the Sector column
python_commits_total$Sector[is.na(python_commits_total$Sector)] <- "Unknown"

# Replace NA values in the Institution column
python_commits_total$Institution[is.na(python_commits_total$Institution)] <- "Unknown"
```


### Extracting and cleaning Country

The detect_geographies() function from the diverstidy package is used to extract country information for users in the commits dataframe with the inputs location, login, and email. There is some further cleaning done to space out text for multiple countries for a given user, and those detecting the country "Jersey" are replaced with United States, as this is referring to New Jersey. Finally, NAs are replaced with Unknown. 

```{r, eval=FALSE}
## rename inputs for detect_geographies()
python_commits_total <- python_commits_total %>%
  rename(
    location = author_user_location,
    login = author_user_login,
    email = author_email
  )

## replace NA with character NA 
python_commits_total$location[is.na(python_commits_total$location)] <- "NA"
              
## extract country
python_commits_total <- python_commits_total %>%
                detect_geographies(login, 
                location, "country", email)

### split on "|" and filter for unique countries identified 
python_commits_total <- python_commits_total %>%
  mutate(
    country_fixed = strsplit(as.character(country), split = "\\|") %>%   # Split on "|"
      map(~unique(.)) %>%                                         # Keep only unique values
      sapply(paste, collapse = ",")                               # Collapse back into a string
  )

### replace with NA for countries that had multiple false identified
python_commits_total$country_fixed <- ifelse(
  sapply(gsub("[^,]", "", python_commits_total$country_fixed), nchar) > 5,
  NA,
  python_commits_total$country_fixed
)


python_commits_total <- python_commits_total %>%
  mutate(
    country_fixed = strsplit(country_fixed, split = ",") %>%  # Split on comma
      map(~ .[!. %in% "NA"]) %>%                             # Remove "NA" values (note the space before "NA")
      sapply(paste, collapse = ",")                           # Collapse back into a string
  )

### Replace any instances of new jersey being identified as jersey with united states
python_commits_total$country_fixed <- gsub("^Jersey, United States$|^United States, Jersey$", "United States", python_commits_total$country_fixed)


### replace NA, blank, or character NA with Unknown

# Replace NA values, "NA" strings, and blanks with "Unknown"
python_commits_total$country_fixed <- ifelse(is.na(python_commits_total$country_fixed) | 
                                             python_commits_total$country_fixed == "NA" | 
                                             python_commits_total$country_fixed == "", 
                                             "Unknown", 
                                             python_commits_total$country_fixed)

```

### Prepare and save dataset for analysis

Now that the commits data has user organization, sector, and country data, it is joined to the dependency and repo level data to generate a final dataframe that will be used for analysis. 

```{r, eval=FALSE}
### join  repo, commit, package, and dependency data
python_full <- python_commits_total %>%
                left_join(python_repos, by = "slug")%>%
                left_join(python_dependencies, by = "slug")

### create "year_created" variable
python_full$year_created <- substr(python_full$created_at, 1, 4)

### create Package variable 
python_final <- python_full %>%
                    select(Package, description, dependencies, slug, year_created, stargazerCount,
                           forkCount, issuesCount, pullRequestsCount, login, email, author_name, author_user_pronouns,
                           author_user_company, location, country_fixed, Institution, 
                           Sector, total_additions)

```


